% Please add the following required packages to your document preamble:
% \usepackage{longtable}
% Note: It may be necessary to compile the document several times to get a multi-page table to line up properly
\begin{longtable}{lp{3cm}p{6cm}}
\caption{Functional requirements for a master-detail Tree editor with property sheet.}
\label{tab:function-requirements}\\
\multicolumn{1}{c}{\textbf{ID}} &
  \multicolumn{1}{c}{\textbf{Requirement}} &
  \multicolumn{1}{c}{\textbf{Description}} \\ \hline
\endfirsthead
%
\multicolumn{3}{c}%
{{\bfseries Table \thetable\ continued from previous page}} \\
\multicolumn{1}{c}{\textbf{ID}} &
  \multicolumn{1}{c}{\textbf{Requirement}} &
  \multicolumn{1}{c}{\textbf{Description}} \\ \hline
\endhead
%
FR1 &
  Provide an interactive Tree Editor in VSCode and Theia (Gitpod) &
  \begin{tabular}[c]{@{}p{6cm}@{}}The software must use an extension mechanism to provide a custom editor for trees.\\ A textual representation is not sufficient.\\ The tree comprises a hierarchy of nodes and their child nodes.\end{tabular} \\
FR2 &
  Provide an interactive Property sheet in VSCode and Theia (Gitpod) &
  \begin{tabular}[c]{@{}p{6cm}@{}}The software must use an extension mechanism to provide a custom property sheet for tree nodes.\\ The property sheet needs to be synchronized with the selected node in the tree editor.\end{tabular} \\
FR3 &
  Provide an action bar with dynamically provided actions in VSCode and Theia (Gitpod). &
  The action bar should have actions that are specified by a backend Tree Language Server. \\
FR4 &
  The Tree must view nodes with labels and icons. &
  \begin{tabular}[c]{@{}p{6cm}@{}}Every node should have a default icon that depends on its node "type".\\ Every node should have a name that is read from the node data.\end{tabular} \\
FR5 &
  Tree nodes with children can toggle the visibility of children by user interaction. &
  \begin{tabular}[c]{@{}p{6cm}@{}}An icon or symbol will show if a node has children.\\ If the user interacts with this icon, e.g. a click, all the children will toggle their visibility on/off.\end{tabular} \\
FR6 &
  The Tree and Property views update automatically when the underlying model changes. &
  Subscribe to change notifications from the Model Server, in the Tree Language Server. \\
FR7 &
  The Action Bar updates when the tree selection changes. &
  Show the available actions for the newly selected node. \\
FR8 &
  Support creation of new nodes. &
   \\
FR9 &
  Support deletion of existing nodes. &
   \\
FR10 &
  Support selecting a node. &
   \\
 &
   &
  
\end{longtable}