\subsection{Actors}

This section will present some of the main actors in the \acrlong{emf} ecosystem.
Most of the technologies discussed in \cref{sec:technologies} are developed by these actors.
Some of the technologies are mentioned by name here, and will be discussed later on.

\paragraph*{Eclipse Foundation} % EMF, Theia
An independent not-for-profit corporation created in 2004.
It aims to serve the Eclipse community, which sprung out from the \emph{Eclipse Project} created by IBM in 2001.~\cite{m.milinkovichEclipseFoundationEclipse2005}
Many \gls{open source} projects are hosted under the Eclipse Foundation.

\paragraph*{Obeo} % Sirius, Eclipse Ecore Tools
Specializes in tailoring \gls{open source} modeling solutions to clients.~\cite{ObeoFewWords}
Contributes to Eclipse Foundation projects like Sirius, Acceleo, Ecore Tools.~\cite{ObeoProductsPresentation}

\paragraph*{EclipseSource} % EMF Forms, JSON Forms, EMF Json? GLSP, Sprotty, Theia
Develops products and tools for engineers.~\cite{eclipsesourceServices}
Contributes to Eclipse Foundation projects like GLSP, Sprotty, Theia, EMF Forms, EMF.Cloud.~\cite{guindonEclipseMembershipEclipseSource}

\paragraph*{TypeFox} % Theia, Gitpod, Sprotty
Aims to help businesses and enigneers by providing software tools.~\cite{typefoxTypeFoxSmartTools}
The original creator of Theia and Gitpod.

\paragraph*{RedHat} % Che, Theia
A provider of enterprise \gls{open source} solutions.
Specializes in linux, \gls{cloud} and \gls{Kubernetes}.~\cite{redhatWorldOpenSource}
Creators of Che, and contributes to Theia.

\paragraph*{Microsoft}
The original creators of \gls{VSCode}, a text editor based on web technology.
Microsoft is not a big actor in the modeling world.
They are only relevant here because of \gls{VSCode}.
They decide which \acrshortpl{API} to support (which \gls{Theia} may have to implement).
Microsoft do not consider the \acrshort{emf} or \gls{Theia} developers when  making choices. % VSCode
