\section{Context}

%Software engineering + modeling
Software engineering is a broad field. It has multiple approaches to methodology, programming languages, practices and paradigms.
One approach to developing software systems is to model a domain.
The domain is usually a phenomena in the real world which a business is interested in. And the conceptual model is an abstraction of this domain, where essential actors, entities, properties and relationships are formalized.

% MDSE, MDD, MBD
This conceptual model can be utilized by the engineers to various degrees.
It could simply document the domain in order to help understanding and communication among those working with the domain. Or the model could be the basis of a software system. The software could be generated automatically based on the model, or an interpreting system could execute the model itself.

% MDD
When the model itself is the source of truth for software, the model is \textit{driving} the development. This is called \acrfull{mdd}. Changes to the domain result in changes to the model, before changing the system's code. And the code itself is \textit{derived from the model}, often using model-to-text transformations. Oftentimes a \textit{complete} system can not be generated, and a programmer is required to manually code some details or rules of the domain into the generated code.

% Education of MDD
The concepts and tools used in \acrshort{mdd} are being taught to software engineering students.
Not all curriculums include \acrshort{mdd}, as it is mostly relevant for specializations in Software Development. %Skip sentence?
Development using models is very reliant on tools. One of the tools that students learn is the \acrfull{emf} and its \gls{metamodel} called \gls{Ecore}.

% EMF details

% Issues with EMF
Despite \acrshort{emf} being a great framework, its tight integration with \gls{Eclipse} harms the adoption. Some students have a negative attitude against \gls{Eclipse}, and learning about its architecture feels like wasted time.
\textcite{kuzniarzTeachingModelDrivenSoftware2016} found that students resist when the technology and skills are not used in other courses.
A general problem for \acrshort{mdd} adoption identified by \textcite{jonwhittleTaxonomyToolrelatedIssues2015} was a low impact on personal career needs. 
The students look to the industry, and mostly find mentions of ``IntelliJ, React, Typescript, Scrum, AI'', never Eclipse. They forget that much of the popular technologies are hype driven, and not the only tools used.
\textcite[p.~21--23]{brambillaModelDrivenSoftwareEngineering2017} claims that model-driven software engineering has passed the peak of the hype curve, and is now in the ``slope of enlightenment''. This means \acrshort{mdd} is not dead, but rather that we are only now seeing how it is best used.\footnote{Compare this to how the hyped Blockchain was supposed to fix every problem, but now we see it doesn't solve much at all.} 

% My proposal

%TODO

% Related works and their shortcomings


